---
<<<<<<< HEAD
title: "PeerAssessment_1"
author: "KP"
date: "Sunday, June 14, 2015"
output: html_document
---

```{r setoptions, echo=TRUE}
library(knitr)
library(rmarkdown)
library(plyr)
library(dplyr)
library(utils)
opts_chunk$set(echo=TRUE)
```

## Loading and preprocessing the data
```{r loaddata}
fileUrl <- "http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(fileUrl, destfile="./repdata-data-activity.zip", mode="wb")
unzip("./repdata-data-activity.zip")
activity <- read.csv(file="./activity.csv")
```

## What is mean total number of steps taken per day?
```{r stats+hist, fig.height=4, fig.width=6}
library(plyr)
dailytotals <- ddply(activity, .(date), summarize, total_steps=sum(steps))
hist(dailytotals$total_steps, 
        breaks=25, 
        main="Histogram of Total Steps each day",
        xlab ="Total Steps")
mean_daily_steps <- mean(dailytotals$total_steps, na.rm=TRUE)
median_daily_steps <- median(dailytotals$total_steps, na.rm=TRUE)
```

## What is the average daily activity pattern?
```{r timeseries, fig.height=4, fig.width=6}
intervaltotals <- ddply(activity, .(interval), summarize, avg_steps=mean(steps, na.rm=TRUE))
int_totals <- arrange(intervaltotals, as.numeric(interval))
with(int_totals, 
        plot(interval,avg_steps, type="l",
        main="Average steps during an interval",
        ylab= "Average steps"))
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?


=======
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data



## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
>>>>>>> 80edf39c3bb508fee88e3394542f967dd3fd3270
